Permits, permit holders, vessels 2

### 2016-04-13 Create_Summary_Tables_AllFishingActivities.Rmd
Update Create_Summary_Tables_AllFishingActivities.Rmd

>>>>

## This file summarizes the cfec catch data into a few different objects. These objects contain p_holder annual summaries of landed pounds and earnings by gear type, area fished and by species. Both wide and long formats are provided for easier modeling / plotting. The output of this file is an RData image called "cfecModelsetup.RData."
